Analysis

### 2022-06-06 EDA_liftOver_mm.Rmd
mm liftOver

# Input files
fileNameIn1 <- file.path(dir_data, "sample_annotation.csv")
# Output files
fileNameOut1 <- file.path(dir_data, "Figure_liftOverJaccard.svg")
```

@@

```{r}
# Adjust clustering method
# if(genome_assembly == "hg38") {
#   clust_method <- "euclidean"
# }
# if(genome_assembly == "mm10") {
#   clust_method <- "correlation"
# }
clust_method <- "euclidean"
# Save the plot
col3 <- colorRampPalette(c('white', 'white','white','white','white','white','white','orangered'))(20)
# all.equal(colnames(mtx_to_plot), sample_annotation$Name)
mydf <- data.frame(Assembly = sample_annotation$Assembly)
rownames(mydf) <- sample_annotation$Name
# png("man/figures/excluderanges_hg38_jaccard.png", width = 1000, height = 900, res = 200)
p <- pheatmap(data.matrix(mtx_to_plot), cluster_cols = T, cluster_rows = T, color = col3,
         clustering_method = "ward.D",# "ward.D", 
         clustering_distance_rows = clust_method, 
         clustering_distance_cols = clust_method, 
         annotation_row = mydf, annotation_colors = list(Assembly = c(hg18 = mycols[2], hg19 = mycols[4], hg38 = mycols[5], T2T = mycols[1])),
         treeheight_row = 40,
         treeheight_col = 0, 
         display_numbers = TRUE)

>>>>

# Input files
fileNameIn1 <- file.path(dir_data, "sample_annotation_mm.csv")
# Output files
fileNameOut1 <- file.path(dir_data, "Figure_liftOverJaccard_mm.svg")
```

@@

```{r}
# Adjust clustering method
# if(genome_assembly == "hg38") {
#   clust_method <- "euclidean"
# }
# if(genome_assembly == "mm10") {
#   clust_method <- "correlation"
# }
clust_method <- "euclidean"
# Save the plot
col3 <- colorRampPalette(c('white', 'white','white','white','white','white','white','orangered'))(20)
# all.equal(colnames(mtx_to_plot), sample_annotation$Name)
mydf <- data.frame(Assembly = sample_annotation$Assembly)
rownames(mydf) <- sample_annotation$Name
# png("man/figures/excluderanges_hg38_jaccard.png", width = 1000, height = 900, res = 200)
p <- pheatmap(data.matrix(mtx_to_plot), cluster_cols = T, cluster_rows = T, color = col3,
         clustering_method = "ward.D",# "ward.D", 
         clustering_distance_rows = clust_method, 
         clustering_distance_cols = clust_method, 
         annotation_row = mydf, annotation_colors = list(Assembly = c(mm9 = mycols[2], mm10 = mycols[4])),
         treeheight_row = 40,
         treeheight_col = 0, 
         display_numbers = TRUE)
